### 2024-08-08 machine-learning.qmd
20240802 - check for duplicates
20240808 - notes

nfl_advancedStatsPFR_seasonal %>% 
  group_by(gsis_id, season) %>% 
  filter(n() > 1) %>% 
  head()
```

@@

(CONSIDER WIDENING THE DATA TO AVOID MULTILEVEL IMPUTATION)

>>>>

nfl_advancedStatsPFR_seasonal %>% 
  group_by(gsis_id, season, team) %>% 
  filter(n() > 1, !is.na(gsis_id)) %>% 
  select(gsis_id, pfr_id, season, team, everything()) %>% 
  head()
```

@@

NOTES:

- CONSIDER WIDENING THE DATA TO AVOID MULTILEVEL IMPUTATION
- IMPUTE THE TRAINING AND TEST DATA SEPARATELY
